GVN-hoist: hoisting expressions from control flow

### 2016-08-04 hoist.tex
loads stores

\subsection{Hoisting stores}
We need to value number the address and the value being stored.

>>>>

\subsection{Hoisting loads}
In order to value number stores, we value number (hash) the address from where
the value is to be loaded. Then we need to compute the hoisting point just like
we did for the scalars. At the hoisting point we compute if the operands to the
load (an address) is available. If it is not available we can try to compute the
addresss if that is possible.  Along the path from current position of the load
instruction through the hoiting point, we find if there are aliasing stores, we
find if any of the basic blocks are landing pads or targets of indirect
branches. In those cases we discard the candidate. Since the load increases the
register pressure by one (unless the operand to load becomes dead at the load),
we evaluate if it is beneficial to hoist the load.

\subsection{Hoisting stores}
In order to value number stores, we value number (hash) the address as well as
the value to be stored to that address. For the legality, we need to check the
dependency requirements just like hoisting loads. We need to check that the
operands of store are available at the hoisting point, that there are no
aliasing loads or store along the path from the current position through the
hoisting point and, none of the basic blocks along the path are landing pads.
Once all the legality checks are satisfied, it is a good candidate to be
hoisted.
